Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-02-28 paper.tex
okay

Correctly identifying protein posttranslational-modifications (PTMs) is crucial to understanding many aspects of protein function in biological processes. Methods to identify and localize PTMs from complex biological samples have been limited, but a few techniques are emerging. G-PTM-D\cite{Li_2016} is a recently developed tool for global identification of PTMs. Spectra file calibration prior to applying the tool, and algorithmic improvements in the peptide database search greatly improve the accuracy and efficiency of new PTM identification. We enhanced G-PTM-D by using non-standard mass-window searches, and demonstrate its effectiveness in identification of numerous types of PTMs, including high-mass modifications such as glycosylations. The number of identified modifications increased by 20\% and the search time decreased by an order of magnitude. We also show the advantages of using mass-window searches in other contexts, when PTM discovery is not the primary goal.
\end{abstract}

>>>>

Correct identification of protein posttranslational-modifications (PTMs) is crucial to understanding many aspects of protein function in biological processes. G-PTM-D\cite{Li_2016} is a recently developed tool for global identification of PTMs. Spectral file calibration prior to applying the tool, and algorithmic improvements in the peptide database search greatly improve the accuracy and efficiency of PTM identification. We enhanced G-PTM-D by using targeted mass-window searches, and demonstrate its effectiveness in identification of numerous types of PTMs, including high-mass modifications such as glycosylations. The proposed changes lead to a 20\% increase in the number of identified modifications and an order of magnitude decrease in the search time. Additional advantages of using targeted mass-windows searches in context of novel modification discovery are shown.
\end{abstract}
